Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-17 ieee_paper.tex
Updated figures.

\begin{figure}[t]
  \centering
  \subfigure[Supercompact]{\includegraphics[width=.48\linewidth]{figures/supercompact_max_perf.pdf}}
  \subfigure[Compact]{\includegraphics[width=.48\linewidth]{figures/compact_max_perf.pdf}} \\
  \subfigure[Random]{\includegraphics[width=.48\linewidth]{figures/random_max_perf.pdf}}
  \subfigure[RBF 3D]{\includegraphics[width=.48\linewidth]{figures/rbf_max_perf_run1.pdf}}
  \caption{Performance of "best code" accross instance types. \todo{Why stop at 1.6M
      rows. Is that because of memory limitation? I guess that's what
      it is}}
\end{figure}

>>>>

\begin{figure*}[t]
  \centering
  \subfigure[Supercompact and random.]{\includegraphics[width=.48\linewidth]{figures/random_supercompact.pdf}}
  \subfigure[Compact and RBF-FD]{\includegraphics[width=.48\linewidth]{figures/rbf_compact.pdf}}

  %\subfigure[Supercompact]{\includegraphics[width=.48\linewidth]{figures/supercompact_max_perf.pdf}}
  %\subfigure[Compact]{\includegraphics[width=.48\linewidth]{figures/compact_max_perf.pdf}} \\
  %\subfigure[Random]{\includegraphics[width=.48\linewidth]{figures/random_max_perf.pdf}}
  %\subfigure[RBF 3D]{\includegraphics[width=.48\linewidth]{figures/rbf_max_perf_run1.pdf}}
  \caption{Performance of "best code" accross instance types. \todo{Why stop at 1.6M
      rows. Is that because of memory limitation? I guess that's what
      it is}}
\end{figure*}
